---
title: "Analysis 5A"
author: "Randall Hendrickson"
date: "December 5, 2017"
output: 
   html_document:
      keep_md: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Procrastination Analysis

```{r analysis}
library(here)
library(knitr)
library(kableExtra)
script1 <- here("scripts", "AnalysisMikeQ5.R")
read_chunk(script1)
```


```{r analysis_header}

# The Procrastination Analysis script wrapped in a RMD document

```

## Question 5

#### The Top 15 Nations in Average AIP Score
Macau, Taiwan, Dominican Republic, Cyprus, Qatar, Panama, Puerto Rico, Iceland, Ecuador, Sri Lanka, Columbia, Kenya, Turkey, Uruguay, France

#### The Top 15 Nations in Average GP Score
Taiwan, Puerto Rico, Qatar, Panama, Myanmar, Sri Lanka, Poland, Austria, Turkey, Ecuador, France, Malaysia, Slovenia, Uruguay, Iceland

#### The following Nations appear in both Top 15 Nations in AIP and Top 15 Nations in GP
Ecuador, France, Iceland, Panama, Puerto Rico, Qatar, Sri Lanka, Taiwan, Turkey, Uruguay 

#### There is a relationship and trend between Age and Income. The older the Age, the higher the income.

#### There doesn't seem to be a discernible relationship between Life Satisfaction and HDI.



```{r analysis_mike_q5_a}
## @knitr analysis_mike_q5_a
```

### Reproducible research show sessionInfo

```{r sessionInfo}
sessionInfo()
```
